---
title: "Assignment 1"
---

My first assignment has two parts.

## (a)

I watched the Model Migration: from Excel to R video by Johnny Breen. In the video, he explains that one day his boss gave him the task of transferring data from Excel to R and he tells about his experiences while doing this task. He says that many companies maintain a large number of legacy models in the Excel platform, and with the advent of data analytics, these companies are looking for ways to migrate their existing models from the Excel environment to the R environment. He shares his experiences about the difficulties that future analysts may encounter in this model transition process and gives 3 main recommendations. These are: 1) Don't copy Excel :) 2)Structure your model 3) Keep things simple.

## (b)

**1)** Code blocks are created by aligning in Python. In R, curly brackets are used.

```{r}
#y = 3
#if y > 5:
#    print("y value is greater than 5.")
#else:
#    print("The y value is less than or equal to 5.")
```

```{r}
#y <- 3
#if (y > 5) {
#  print("y value is greater than 5.")
#} else {
#  print("The y value is less than or equal to 5.")
#}
```

**2)** In Python, the first element of a list is index \[0\]. In R, the first element is index \[1\].

```{r}
#l = ['a', 'b', 'c', 'd', 'e']
#print(l[0])
```

```{r}
#v <- c('a', 'b', 'c', 'd', 'e')
#print(v[1])
```

both codes above return a

**3)** R is used more extensively in statistics and data analytics than Python. Because R includes data frames, statistical models and packages. Examples of these statistical models and packages:

Statistical Models: Linear Regression, Logistic Regression, Decision Trees, Random Forests, Support Vector Machines

Packages: dplyr, ggplot2, tidyr, caret, stats

(AI)

## **(c)**

```{r}
library(dslabs)
data("na_example")
print(na_example)
number_of_na <- sum(is.na(na_example))
print(number_of_na)
new_na_example <- na_example
na_example[is.na(na_example)] <- 0
print(na_example)
print(sum(is.na(na_example)))
```
